### 2021-05-14 README.Rmd
Fix DOI formatting

> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW) *Global Policy* (forthcoming), doi:[10.1111/1758-5899.12984](https://doi.org/10.1111/1758-5899.12984)

>>>>

> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW) *Global Policy* (forthcoming), doi: [`10.1111/1758-5899.12984`](https://doi.org/10.1111/1758-5899.12984)
